---
title: "Using R to Track Two-Level Demographic Stratification"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br>

#### HOW TO USE THIS DOCUMENT:
This R Notebook (.rmd) contains chunks of runnable code along with detailed analysis and documentation of the code and workflow. To use this Notebook, render (knit) it as an HTML document into the RStudio Viewer Pane:

1. In RStudio Preferences, R Markdown section, set the `Show output preview in:` option to `Viewer Pane`.
2. Knit the notebook using `File -> Knit Document`. This will produce a readable HTML version of this document in the Viewer Pane. 
3. Close this Notebook (once you have the HTML in the Viewer, you no longer need the Notebook).
4. Open a new R script in the Source Pane. This will serve as your working script, into which you can copy-and-paste code from the HTML.

The HTML narrative is organized into sections reflecting discrete topics and operations in the R workflow. Each section has two parts:

1. `VALID CODE TO RUN`: this code can be copy-and-pasted into your working R script. All file paths are relative to your R project folder.
2. `COMMENTED CODE CHUNKS`: these snippets provide the analysis and documentation of the code and workflow. The R code in these snippets is redundant with that in `VALID CODE TO RUN` section. Here, it serves merely to enhance the code documenatation, and is not meant to be run.

<br>

#### UTILIZING RStudio PROJECTS AND DIRECTORY PATHS:
To keep your work organized, set up a project in RStudio, by clicking File -> New Project. You'll be asked to specify a working directory associated with the project. To facilitate running the code of this project easily, locate input files in a folder named `INPUT-FILES`, within the working directory associated with this project. Also, create a folder named `OUTPUT-FILES`, within the working directory associated with this project.

<br>

#### PACKAGES

Packages are the add-on features and functions that give R its power and versatility. To use the code in this notebook, install and load these packages:

###### VALID CODE TO RUN
```{r packages, message=FALSE}
suppressMessages(library(here))
suppressMessages(suppressWarnings(library(data.table)))
suppressMessages(suppressWarnings(library(tidyverse)))
```
Note use of `suppressMessages` and `suppressWarnings` to silence chatter on the console.

<br>

#### CODE OVERVIEW
This script takes as input .csv files downloaded from Survey Monkey containing demographic information for each case in a research sample. The script is set up to read in a static file of cases collected up to a certain timepoint, followed by a separate dynamic file of cases collected from that timepoint up to the present, and combine the two into a single input file. Required columns for the input files are: ID, form, zipcode, ageyear, gender, PEL, hispanic, and ethnicity.

The data are recoded and processed to fill a demographic tracking table in which gender, PEL, race, and region are tabulated separately for each level of age stratification. All cells are filled simultaneously, allowing the data administer to evaluate whether potential incoming cases meet the remaining demographic needs of the sample. For each level of each demographic variable, output columns include number of cases collected, number of cases still neeeded, and the census percentage for that demographic value at that age level. The script generates separate output tables for each test form, saving tables as .csv in the `OUTPUT-FILES` folder.

<br>

#### Read in and recode .csv input data from a static data set

###### VALID CODE TO RUN
```{r static_input_read, eval=FALSE}
old_demos_input <-
  suppressMessages(suppressWarnings(read_csv(here(
    'TOD-ANNIKA/INPUT-FILES/TOD-old-demo-survey-2019-05-22.csv'
  )))) %>% filter(!is.na(.[1])) %>% select(
    10,
    11,
    12,
    14,
    15,
    16,
    17,
    18,
    19
  )

attributes(old_demos_input) <- NULL
names(old_demos_input) <- c("IDnum", "form", "zip", "ageyear", "grade", "gender", "PEL", "hispanic", "ethnic")
old_demos_input_2019_05_22 <- old_demos_input %>% enframe() %>% unnest() %>% unstack(value ~ name) %>% 
  select(IDnum, form, zip, ageyear, grade, gender, PEL, hispanic, ethnic) %>% 
  mutate_at(vars(IDnum, zip, ageyear), as.integer) %>% 
  mutate(
    agestrat = case_when(
      ageyear == 5 ~ "05",
      ageyear == 6 ~ "06",
      ageyear == 7 ~ "07",
      ageyear == 8 ~ "08",
      ageyear == 9 ~ "09",
      ageyear >= 10 & ageyear <= 24 ~ as.character(ageyear),
      ageyear >= 25 & ageyear <= 40 ~ "2540",
      ageyear >= 41 & ageyear <= 50 ~ "4150",
      ageyear >= 51 & ageyear <= 60 ~ "5160",
      ageyear >= 61 & ageyear <= 70 ~ "6170",
      ageyear >= 71 & ageyear <= 80 ~ "7180",
      ageyear >= 81 & ageyear <= 90 ~ "8190",
      TRUE ~ NA_character_
    ),
    form1 = case_when(
      form == "TOD-S + TOD-E" ~ "TOD_E",
      form == "TOD-S + TOD" ~ "TOD",
      TRUE ~ NA_character_
    ),
    PEL1 = case_when(
      PEL == "Less than HS" ~ "Less_than_HS",
      PEL == "High School" ~ "HS_degree",
      PEL == "Some College (including Associate's Degree)" ~ "Some_college",
      PEL == "Bachelors Degree (or higher)" ~ "BA_plus",
      TRUE ~ NA_character_
    ),
    ethnic1 = case_when(hispanic == "Yes" ~ "Hispanic",
                        ethnic == "White or Caucasian" & hispanic == "No" ~ "White",
                        ethnic == "Black or African American" & hispanic == "No" ~ "Black",
                        ethnic == "Asian or Asian American" & hispanic == "No" ~ "Asian",
                        (ethnic == "Other / Multiracial" | ethnic == "American Indian or Alaska Native" | 
                           ethnic == "Native Hawaiian or other Pacific Islander") & hispanic == "No" ~ "Other",
                        TRUE ~ NA_character_),
    region = case_when(
      inrange(zip, 1000, 8999) | inrange(zip, 10000, 19699) ~ "Northeast",
      inrange(zip, 900, 999) |
        inrange(zip,
                19700,
                33999) |
        inrange(zip,
                34100,
                42799) |
        inrange(zip, 70000, 79999) |
        inrange(zip, 88500, 88599) ~ "South",
      inrange(zip, 43000, 58999) |
        inrange(zip, 60000, 69999) ~ "Midwest",
      inrange(zip, 59000, 59999) |
        inrange(zip,
                80000,
                88499) |
        inrange(zip,
                88900,
                96199) |
        inrange(zip, 96700, 96899) |
        inrange(zip, 97000, 99999) ~ "West",
      TRUE ~ NA_character_
    )
  ) %>% select(IDnum, form1, ageyear, agestrat, gender, PEL1, ethnic1, region) %>% rename(form = form1, ethnic = ethnic1, PEL = PEL1)
```

###### COMMENTED CODE CHUNKS
Input .csv is read in and assigned to `old_demos_input`. These data are piped into `filter`, which keeps rows identified by `!is.na(.[1])`, i.e., it keeps rows that are NOT missing on the first column `[1]` of the piped table `.`. `select` keeps only certain columns, identified by their numerical position number from left to right within the piped table.
```{r static_input_read, echo=1:14, eval=FALSE}
```
Tables downloaded from Survey Monkey come loaded with garbage attributes that R picks up. Next snippet removes these attributes, first by assigning a `NULL` value to them using `attributes`, which also transforms the nine-column input table into a list of of 9 char vecs, each with a length equal to the number of rows in the input table. These unnamed vectors, which will be transformed back into columns of a data frame, are then given appropriate `names`. 

A new, cleaned up input table `old_demos_input_2019_05_22` is then created by piping the list `old_demos_input` into `enframe()`, which turns the list into a two-column tibble, with a column of names and a list-column containing the nine char vecs. This table is then piped into `unnest()`, which expands it into a tall two-column table (`name` and `value`), in which each row contains a single value of a single variable, repeating through all the values of the first variable, and then continuing down the rows with all the values of the second variable, etc. This table is then piped into `unstack`, which collapses the tall table into a wide table in which each variable has its own named column containing its values.
```{r static_input_read, echo=16:18, eval=FALSE}
```
`select` reorders columns, `mutate_at` converts certain variables to integer format `as.integer`.
```{r static_input_read, echo=19:20, eval=FALSE}
```
`mutate` recodes the demographic variables to desired formats and values, using `case_when` for conditional recoding. General format of `case_when` is to specify the logical condition for applying a code (e.g., `ageyear >= 25 & ageyear <= 40`), and then use the formula symbol `~` to specify the code for that condition. The last line of `case_when` is `TRUE`, which is essentially a blanket "else" condition. `TRUE` must evaluate to the same variable format as the RHS of the other logical conditions. For example, if those conditions yield strings, and you wish `TRUE` to evaluate to `NA`, you would use `NA_character_`, and so forth.

Another function to note in this snippet is `data.table::inrange` which takes three arguments, a variable, lower bound, and upper bound. It evaluates to logical `TRUE` if the value of the var is within the range delineated by the bounds. Those bounds are inclusive by default, they can be set to exclusive using the argument `incbounds = FALSE`.
```{r static_input_read, echo=21:79, eval=FALSE}
```


<br>

#### Read in and recode .csv input data from a dynamic, newly-updated data set

The code below is analogous to the code in the previous section, so it will NOT be analyzed and documented separately.

At the end of the code section below, the two input tables are joined into a single object `All_demos`, using `dplyr::bind_rows` to stack tables with same columns, different rows on top of one another. Two subsidiary objects, `demos_TOD` and `demos_TOD_E`, are created by filtering `All_demos` by form name.

###### VALID CODE TO RUN
```{r dynamic_input_read, eval=FALSE}
demos_input <-
  suppressMessages(suppressWarnings(read_csv(here(
    'TOD-ANNIKA/INPUT-FILES/TOD-demos-current-input.csv'
  )))) %>% filter(!is.na(.[1])) %>% select(
    10,
    12,
    13,
    15,
    23,
    16,
    22,
    20,
    21
  )

attributes(demos_input) <- NULL
names(demos_input) <- c("IDnum", "form", "zip", "ageyear", "grade", "gender", "PEL", "hispanic", "ethnic")
current_demos_input <- demos_input %>% enframe() %>% unnest() %>% unstack(value ~ name) %>% 
  select(IDnum, form, zip, ageyear, grade, gender, PEL, hispanic, ethnic) %>% 
  mutate_at(vars(IDnum, zip, ageyear), as.integer) %>% 
  mutate(
    agestrat = case_when(
      ageyear == 5 ~ "05",
      ageyear == 6 ~ "06",
      ageyear == 7 ~ "07",
      ageyear == 8 ~ "08",
      ageyear == 9 ~ "09",
      ageyear >= 10 & ageyear <= 24 ~ as.character(ageyear),
      ageyear >= 25 & ageyear <= 40 ~ "2540",
      ageyear >= 41 & ageyear <= 50 ~ "4150",
      ageyear >= 51 & ageyear <= 60 ~ "5160",
      ageyear >= 61 & ageyear <= 70 ~ "6170",
      ageyear >= 71 & ageyear <= 80 ~ "7180",
      ageyear >= 81 & ageyear <= 90 ~ "8190",
      TRUE ~ NA_character_
    ),
    form1 = case_when(
      form == "TOD-S + TOD-E" ~ "TOD_E",
      form == "TOD-S + TOD" ~ "TOD",
      TRUE ~ NA_character_
    ),
    PEL1 = case_when(
      PEL == "Did not complete high school" ~ "Less_than_HS",
      PEL == "High school graduate/GED" ~ "HS_degree",
      PEL == "Some College or associate's degree" ~ "Some_college",
      PEL == "Bachelors degree or higher" ~ "BA_plus",
      TRUE ~ NA_character_
    ),
    ethnic1 = case_when(hispanic == "Yes" ~ "Hispanic",
                        ethnic == "White" & hispanic == "No" ~ "White",
                        ethnic == "Black/African American" & hispanic == "No" ~ "Black",
                        ethnic == "Asian" & hispanic == "No" ~ "Asian",
                        (ethnic == "Other / Multiracial" | ethnic == "American Indian/Alaska Native" | 
                           ethnic == "Native Hawaiian/Pacific Islander") & hispanic == "No" ~ "Other",
                        TRUE ~ NA_character_),
    region = case_when(
      inrange(zip, 1000, 8999) | inrange(zip, 10000, 19699) ~ "Northeast",
      inrange(zip, 900, 999) |
        inrange(zip,
                19700,
                33999) |
        inrange(zip,
                34100,
                42799) |
        inrange(zip, 70000, 79999) |
        inrange(zip, 88500, 88599) ~ "South",
      inrange(zip, 43000, 58999) |
        inrange(zip, 60000, 69999) ~ "Midwest",
      inrange(zip, 59000, 59999) |
        inrange(zip,
                80000,
                88499) |
        inrange(zip,
                88900,
                96199) |
        inrange(zip, 96700, 96899) |
        inrange(zip, 97000, 99999) ~ "West",
      TRUE ~ NA_character_
    )
  ) %>% select(IDnum, form1, ageyear, agestrat, gender, PEL1, ethnic1, region) %>% rename(form = form1, ethnic = ethnic1, PEL = PEL1)

All_demos <- bind_rows(current_demos_input, old_demos_input_2019_05_22) %>%
  arrange(agestrat, ageyear, IDnum) %>% group_by(agestrat)

demos_TOD <- All_demos %>% filter(form == "TOD")
demos_TOD_E <- All_demos %>% filter(form == "TOD_E")
```

<br>

#### Initialize static columns for output table

###### VALID CODE TO RUN
```{r static_columns, eval=FALSE}
static_columns_TOD <-
  bind_cols(
    tibble(
      agestrat = c(
        "05",
        "06",
        "07",
        "08",
        "09",
        "10",
        "11",
        "12",
        "13",
        "14",
        "15",
        "16",
        "17",
        "18",
        "19",
        "20",
        "21",
        "22",
        "23",
        "24",
        "2540",
        "4150",
        "5160",
        "6170",
        "7180",
        "8190"
      )
    ),
    fread(here("DATA/STATIC_COLUMNS/TOD_Target_n_by_age.csv"), select = c("target_n")),
    (
      fread(
        here("DATA/STATIC_COLUMNS/Age_x_gender_TOD_final.csv"),
        select = c("Male", "Female")
      ) %>%
        rename(Male_census_pct = Male, Female_census_pct = Female)
    ),
    (
      fread(
        here("DATA/STATIC_COLUMNS/Age_x_PEL_TOD_final.csv"),
        select = c("Less_than_HS", "HS_Degree", "Some_College", "BA_or_Higher")
      ) %>%
        rename(
          Less_than_HS_census_pct = Less_than_HS,
          HS_degree_census_pct = HS_Degree,
          Some_college_census_pct = Some_College,
          BA_plus_census_pct = BA_or_Higher
        )
    ),
    (
      fread(
        here("DATA/STATIC_COLUMNS/Age_x_race_TOD_final.csv"),
        select = c("White", "Black", "Asian", "Other", "Hispanic")
      ) %>%
        rename(
          White_census_pct = White,
          Black_census_pct = Black,
          Asian_census_pct = Asian,
          Other_census_pct = Other,
          Hispanic_census_pct = Hispanic
        ) %>%
        select(
          Hispanic_census_pct,
          Asian_census_pct,
          Black_census_pct,
          White_census_pct,
          Other_census_pct
        )
    ),
    (
    fread(
      here("DATA/STATIC_COLUMNS/Age_x_region_TOD_final.csv"),
      select = c("Northeast", "Midwest", "South", "West")
    ) %>%
      rename(
        Northeast_census_pct = Northeast,
        Midwest_census_pct = Midwest,
        South_census_pct = South,
        West_census_pct = West
      ) 
  )
)
static_columns_TOD_E <- static_columns_TOD %>% filter(agestrat %in% c("05", "06", "07", "08", "09")) %>% 
  mutate_at(
    vars(target_n), list(~case_when(
      agestrat == "05" ~ 225,
      agestrat == "06" ~ 225,
      agestrat == "07" ~ 225,
      agestrat == "08" ~ 225,
      agestrat == "09" ~ 10,
      TRUE ~ NA_real_
    )))
```

###### COMMENTED CODE CHUNKS
Create a table of static columns `static_columns_TOD` that will be joined to the input data to create final output table. The data object is wrapped in `dplyr::bind_cols()` which joins a series of input vectors and data frames into a single table. In this application, `bind_cols` has no argument specifying an indexing term, so all input objects must be appropriately sorted before being joined.

The left-most column to be joined is a named char vec containing the levels of `agestrat`, wrapped in `tibble` to transform it into a data frame.
```{r static_columns, echo=1:32, eval=FALSE}
```
The next column to be joined `TOD_Target_n_by_age.csv` is read in by `data.table::fread()`. This function allows you to read in a .csv, and using the `select` argument, keep only certain columns from the input `select = c("target_n")`. The code then proceeds to read in the next column to be joined `Age_x_gender_TOD_final.csv`, select only the `Male` and `Female` columns from the input, and then `rename` those columns for the output table. Note that with `dplyr::rename()`, the **new** name appears to the **left** of the equals sign.

The snippet below is follwed by several other similar code blocks that read in columns for PEL, Race, and Region - these will not be documented separately.
```{r static_columns, echo=33:39, eval=FALSE}
```
At this point, a table of static columns `static_columns_TOD` has been assembled for the TOD form of the test. A second table of static columns now needs to be created for the TOD_E form of the test. The next snippet accomplishes with `dplyr::filter()` to retain only the `agestrat` rows needed for the TOD_E, and then modifying the target n's for those age groups with `dplyr::mutate_at`. The `vars(target_n)` argument names the column to be modified, and the recoding is done by using the shorthand `list(~case_when())` to call `dplyr::case_when`. The latter function assigns a new value for `target_n` to each level of `agestrat` present on the static column table `static_columns_TOD_E`.
```{r static_columns, echo=86:95, eval=FALSE}
```

<br>

#### Initialize and format actual demographic count tables, by demographic variable

Recall that previous code created two tables, `demos_TOD` and `demos_TOD_E`, containing the input demographic counts for each test form. The code below reorganizes this dynamic input data into columns suitable for joining with the static columns to create the final output table. The code does this separately for the four demographic variables (gender, PEL, race, and region), creating four interim tables for each form.

###### VALID CODE TO RUN
```{r demo_count, eval=FALSE}
frm <- c("TOD", "TOD_E")
map(
  frm,
  ~
    eval(as.name(paste0("demos_", .x))) %>% ungroup() %>% select(agestrat, gender) %>% filter(gender != "Other") %>%
    count(agestrat, gender) %>%
    add_row(agestrat = NA_character_, gender = "Male", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, gender = "Female", n = NA_integer_) %>% 
    spread(gender, n, fill = 0) %>%
    filter(!is.na(agestrat)) %>% 
    select(agestrat, Male, Female) %>%
    rename(Male_actual = Male, Female_actual = Female) %>%
    assign(paste0("gender_input_", .x), ., envir = .GlobalEnv)
)

map(
  frm,
  ~
    eval(as.name(paste0("demos_", .x))) %>% ungroup() %>% select(agestrat, PEL)  %>%
    count(agestrat, PEL) %>%
    add_row(agestrat = NA_character_, PEL = "Less_than_HS", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, PEL = "HS_degree", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, PEL = "Some_college", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, PEL = "BA_plus", n = NA_integer_) %>% 
    spread(PEL, n, fill = 0) %>%
    filter(!is.na(agestrat)) %>% 
    select(agestrat, Less_than_HS, HS_degree, Some_college, BA_plus) %>%
    rename(
      Less_than_HS_actual = Less_than_HS,
      HS_degree_actual = HS_degree,
      Some_college_actual = Some_college,
      BA_plus_actual = BA_plus) %>% 
    assign(paste0("PEL_input_", .x), ., envir = .GlobalEnv)
)

map(
  frm,
  ~
    eval(as.name(paste0("demos_", .x))) %>% ungroup() %>% select(agestrat, ethnic)  %>%
    count(agestrat, ethnic) %>%
    add_row(agestrat = NA_character_, ethnic = "Hispanic", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, ethnic = "Asian", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, ethnic = "Black", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, ethnic = "White", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, ethnic = "Other", n = NA_integer_) %>% 
    spread(ethnic, n, fill = 0) %>%
    filter(!is.na(agestrat)) %>% 
    select(agestrat, Hispanic, Asian, Black, White, Other) %>%
    rename(
      Hispanic_actual = Hispanic,
      Asian_actual = Asian,
      Black_actual = Black,
      White_actual = White,
      Other_actual = Other) %>% 
    assign(paste0("ethnic_input_", .x), ., envir = .GlobalEnv)
)

map(
  frm,
  ~
    eval(as.name(paste0("demos_", .x))) %>% ungroup() %>% select(agestrat, region)  %>%
    count(agestrat, region) %>%
    add_row(agestrat = NA_character_, region = "Northeast", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, region = "South", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, region = "Midwest", n = NA_integer_) %>% 
    add_row(agestrat = NA_character_, region = "West", n = NA_integer_) %>% 
    spread(region, n, fill = 0) %>%
    filter(!is.na(agestrat)) %>% 
    select(agestrat, Northeast, South, Midwest, West) %>%
    rename(
      Northeast_actual = Northeast,
      South_actual = South,
      Midwest_actual = Midwest,
      West_actual = West) %>% 
    assign(paste0("region_input_", .x), ., envir = .GlobalEnv)
)
```

###### COMMENTED CODE CHUNKS
The snippet below creates the final output columns for the gender data, containing the actual counts of males and females in the study within each agestrat. The snippets for PEL, race, and region are analogous to this one, and so will not be documented separately.

Because there are separate output tables for the TOD and TOD_E test forms, the code initializes a char vec `frm` containing the names of the two forms. `purrr::map()` interates over this vector, creating two distinct output tables. The arguments to `map` are the vector to iterate over `frm`, and an anonymous function to be applied to that vector, designated by the shorthand `~`. Within that function, which constists of a set of functions chained together by the pipe operator `%>%`, `map` substitutes vector elements wherever the token `.x` appears. `map` iterates by running the anonymous function for the first element of `frm`, and then repeating for the second element of `frm`.

`eval(as.name(paste0("demos_", .x)))` provides `map` with the name of the data object to be passed through the pipeline. `paste0` creates the string for the name, by pasting together `demos_` with the element from vector `frm` designated by `.x`. `as.name` coerces that string so that it is evaluated as the name of an object that exists in the global environment (e.g., `demos_TOD`). `eval` forces R to evaluate the string as the name of of a data object that can be piped into a function.

The anonymous function designated by `~` transforms the gender data from the input table (e.g., `demos_TOD`) into columns required for the final output. `ungroup()` removes the previously-applied grouping by agestrat, which would interfere with the operation of subsequent functions. `select()` keeps `agestrat` and `gender` as the only columns piped forward. `filter()` drops rows containing the "Other" gender choice `(gender != "Other")`, so that those cases are not counted in the gender columns of the final output table (note that `filter()` also drops any cases that are missing (`NA`) on gender).

`count()` collapses the data object into a summary table that contains two rows per agestrat, a `Male` row and a `Female` row. It appends a new column `n` that provides counts for each row of the summary table. `add_row()` adds two temporary additional rows, a `Male` row and a `Female` row. These temporary rows are `NA` for `agestrat` and `n`. These temporary rows in the summary table are needed to process input tables where there are no cases yet for a level of a demographic var (e.g., no Asians have yet been endrolled in the study). In this situation, without the temporary rows, the code would fail to generate a column for Asians in the final output tables. Once a study is far advanced enough that there are cases for each level of the demographic level, the `add_row()` lines become superfluous.

`spread()` transforms the data object from a table with a single `gender` column to one with separate `Male` and `Female` columns containing the counts, by `agestrat`, for those values of `gender`. Prior to transformation, the data object has key-value pairs in a key column `gender`, and a value column `n`. `spread()` takes the names of the key and value columns as its first two arguments, and then drops these columns and creates new columns, one for each level of the key variable. The cells in these new `Male` and `Female` columns are populated by the counts from the value column `n`, within each agestrat. The resulting object now has a single row per agestrat, with columns showing the counts of males and females within each agestrat. This is the format required for the final output table. The `fill = 0` argument recodes missing (`NA`) counts to zero, so that all agestrats will be included in the table, even if there are no actual cases in those agestrats yet.


```{r demo_count, echo=1:14, eval=FALSE}
```



spread(): at this point, the data object has key-value pairs in a key column (gender), and a value column (n). n gives the count of cases for each value of gender, within each agestrat. In spread(), the first two arguments give the names of the key and value columns, spread drops these columns and creates new columns, one for each level of the key var. The cells in those columsn are populated by the value from the value column (n) with each agestrat. So the resulting object now has a single row per agestrat,
with columns showing how many males, females and NAs. The `fill = 0` argument recodes missing `NA` counts to zero, so that all agestrats will be included in the table, even if there are no cases in those agestrats yet.
filter() cleans up table by removing an unneeded interim row that is missing on agestrat.
select() keeps only agestrat, Male, and Female columns
rename()provides column names needed for final output table (the actual count of cases received in the agestrat by gender cells)
assign() is required to create an object in the global environment that can be manipulated by downstream code
